Universal Anonymous Signatures

### 2022-07-04 prism-backend/research/gsac/app-uas-proofs.tex
Adding missing file.

\subsection{Correctness and Security of \CUASGen}
\label{ssec:security-uas}

First, we define the \ExtractIssue, \ExtractSign, \IdentifyCred and \IdentifyUK
functions that are needed for some of the properties to be meaningful, in
\figref{fig:helper-funcs}.

\begin{figure}[ht!]
  \begin{minipage}[t]{\textwidth}
    \procedure{$\ExtractIssue(\parm,\utrans)$}{%
      \textrm{Parse \parm as $(\cdot,\cdot,\cdot,\cdot,\NIZKcrs_{\Issue},\cdot,
        \cdot,\cdot)$; $\NIZKcrs_{\Issue}$ as $(\NIZKcrs,\NIZKtrap)$; and
        \utrans as $(\Ccom,\sipk,\cred,\NIZKproof)$} \\
      \pcif \NIZKVerify(\NIZKcrs,\NIZKproof,(\Ccom,\attrs,\sipk)): 
      \pcreturn \bot \\
      (\usk,\scred,\attrs_{\scred}) \gets \NIZKExtract(\NIZKcrs,\NIZKtrap,
      (\Ccom,\attrs,\sipk),\NIZKproof) \\
      \pcreturn (\usk,\attrs,\scred,\attrs_{\scred}) \\
    }

    \procedure{$\ExtractSign(\parm,\oid,\siid,\sig,\yeval,\msg,\feval)$}{%
      \textrm{Parse \parm as $(\cdot,\cdot,\cdot,\cdot,\cdot,\NIZKcrs_{\Sign},
        \cdot,\cdot)$; $\NIZKcrs_{\Sign}$ as $(\NIZKcrs,\NIZKtrap)$; and
        \sig as $(\NIZKproof,\Ec)$} \\
      \textrm{Parse $\PUBOK[\oid]$ as $(\opk,\cdot)$ and let $\sipk \gets
        \PUBIK[\siid]$} \\
      \pcif \NIZKVerify(\NIZKcrs,\NIZKproof,(\msg,\feval,\yeval,\Ec,
      \sipk,\opk)): \pcreturn \bot \\
      (\usk,\scred,\attrs_{\scred},\yinsp,r) \gets \NIZKExtract(\NIZKcrs,
      \NIZKtrap, (\msg,\feval,\yeval^0,\ceval,\cinsp,\sipk,\opk,\widetilde{\Eek}),
      \NIZKproof) \\
      \pcreturn (\usk,\scred,\attrs_{\scred},\yeval^1,\yinsp) \\
    }

    \procedure{$\IdentifyCred(\usk,\attrs_{\cred},\cred)$}{%
      \pcreturn \SBCMVerify(\ipk_{\cred},\cred,\usk,\attrs_{\cred}) \\
    }

    \procedure{$\IdentifyUK(\uid,\usk)$}{%
      \pcif \uid \in \HU: \pcreturn \usk = \UK[\uid] \\
      \pcfor \cid~\suchthat~\CRED[\cid] = (\uid,\cdot,\cdot,\cdot,\cdot,\cdot) \\
      \pcind (\usk',\cdot,\cdot,\cdot) \gets \ExtractIssue(\parm,\trans[\cid]) \\
      \pcind \pcif \usk = \usk': \pcreturn 1 \\
      \pcreturn 0
    }
  \end{minipage}
  \label{fig:helper-funcs}
  \caption{Definition of helper functions \ExtractIssue, \ExtractSign,
    \IdentifyCred, and \IdentifyUK, for \CUASGen.}
\end{figure}

\begin{theorem}[Correctness of \CUASGen]
  \label{thm:correctness-uas}
  If the underlying schemes for commitments, public-key encryption and \SBCM,
  are correct,
  as well as the NIZKs for $\NIZKRel_{\Issue}$, $\NIZKRel_{\Sign}$, and
  $\NIZKRel_{\Open}$, our generic construction \CUASGen satisfies correctness as
  defined in \defref{def:correctness-uas}.
\end{theorem}

@@

\begin{theorem}[Issuance anonymity of \CUASGen]
  \label{thm:iss-anonymity-uas}
  If the NIZK systems used for $\NIZKRel_{\Issue}$ and $\NIZKRel_{\Sign}$ are
  zero-knowledge, our \CUASGen construction satisfies issuance anonymity as
  defined in \defref{def:iss-anonymity-uas}.
\end{theorem}

\begin{proof}[\thmref{thm:iss-anonymity-uas}; Issuance anonymity of \CUASGen]
  We prove the special case in which the adversary makes only one query to the
  \OBTCHALb oracle. The generalization to polynomially many queries follows from
  a standard hybrid argument.

@@

\begin{theorem}[Signature anonymity of \CUASGen]
  \label{thm:sign-anonymity-uas}
  If the NIZK system used for $\NIZKRel_{\Sign}$ is zero-knowledge, and the
  public-key encryption scheme is IND-CCA secure, our \CUASGen construction
  satisfies signature anonymity as defined in \defref{def:sign-anonymity-uas}.
\end{theorem}

\begin{proof}[\thmref{thm:sign-anonymity-uas}; Signature anonymity of \CUASGen]
  \iffalse
  First, we define \SimSetup, \SIMOBTAIN, \SIMSIGN and \SIMOPEN as in
  \figref{fig:anon-sim}.

  \begin{figure}[ht!]
    \begin{minipage}[t]{\textwidth}
      \procedure{$\SimSetup(\secpar,\AttrSpace)$}{%
        \textrm{Parse}~\secpar~\textrm{as}~(\cdot,\secpar_{\NIZK},\cdot,\cdot) \\
        (\NIZKcrs_{\Issue},\NIZKtrap_{\Issue})
        \gets \NIZKSimSetup^{\NIZKRel_{\Issue}}(\secpar_{\NIZK}) \\
        (\NIZKcrs_{\Sign},\NIZKtrap_{\Sign})
        \gets \NIZKSimSetup^{\NIZKRel_{\Sign}}(\secpar_{\NIZK}) \\
        (\NIZKcrs_{\Open},\NIZKtrap_{\Open})
        \gets \NIZKSimSetup^{\NIZKRel_{\Open}}(\secpar_{\NIZK}) \\
        \textrm{Compute}~\parm \gets (\Cparm,\SBCMparm,\Sparm,\Eparm)~
        \textrm{as in}~\Setup \\
        \pcreturn ((\parm,\NIZKcrs_{\Issue},
        \NIZKcrs_{\Sign},\NIZKcrs_{\Open},\AttrSpace),
        (\NIZKtrap_{\Issue},\NIZKtrap_{\Sign},\NIZKtrap_{\Open})) \\
      }

      \begin{minipage}[t]{\textwidth}
        \begin{minipage}[t]{0.55\textwidth}
          \procedure{$\SIMOBTAIN(\cid,\uid,\iid,\attrs,\scid)$}{%
            \pcif \uid \notin \HU: \pcreturn \bot \\
            \pcif \iid \notin \CI: \pcreturn \bot \\
            \pcif \CRED[\cid] \neq \bot: \pcreturn \bot \\
            \sipk_{\scred} \gets \PUBIK[\scid] \\
            \langle \cred, \cdot \rangle \gets
            \langle SimObt(\attrs,\PUBIK[\iid],\sipk_{\scred}),\adv \rangle \\
            \CRED[\cid] \gets (\uid, \cred, \iid, \attrs, \scid, \siid) \\
            \pcreturn \top \\      
          }
        \end{minipage}
        \begin{minipage}[t]{0.45\textwidth}
          \procedure{$SimObt(\attrs,\ipk,\sipk_{\scred})$}{%
            \textrm{Runs $\langle \SBCMCom^{\NIZKRel_{\Issue}},\adv \rangle$} \\
            \pcind \textrm{using $\NIZKSim^{\NIZKRel_{\Issue}}
              (\NIZKcrs_{\Issue},\NIZKtrap_{\Issue},\cdot)$} \\
            \pcind \textrm{instead of $\NIZKProve^{\NIZKRel_{\Issue}}
              (\NIZKcrs_{\Issue},\cdot,\cdot)$}
          }
        \end{minipage}
      \end{minipage}

      \begin{minipage}[t]{\textwidth}
        \begin{minipage}[t]{0.55\textwidth}
          \procedure{$\SIMSIGN(\oid,\uid,\scid,\msg,\feval)$}{%
            \pcif \uid \notin \HU: \pcreturn \bot \\
            \pcif \feval \notin \famfeval: \pcreturn \bot \\
            \Sig \gets SimSign(\PUBOK[\oid],\msg,\feval) \\
            \SIG[\uid] \gets \SIG[\uid] \cup
            \lbrace (\oid,\scid,\Sig,\msg,\feval) \rbrace \\
            \pcreturn \Sig \\
          }
        \end{minipage}
        \begin{minipage}[t]{0.45\textwidth}
          \procedure{$SimSign(\opk,\msg,\feval)$}{%
            \textrm{Like}~\Sign()~\textrm{using} \\
            \pcind \NIZKSim^{\NIZKRel_{\Sign}}(\NIZKcrs_{\Sign},
            \NIZKtrap_{\Sign},\cdot) \\
            \pcind \textrm{instead of}~\NIZKProve^{\NIZKRel_{\Sign}}
            (\NIZKcrs_{\Sign},\cdot,\cdot)        
          }
        \end{minipage}
      \end{minipage}

      \begin{minipage}[t]{\textwidth}
        \begin{minipage}[t]{0.55\textwidth}
          \procedure{$\SIMOPEN(\oid,\Sig,\msg)$}{%
            \textrm{Let}~\uid~\textrm{be s.t.}~(\oid,\scid,\Sig,\msg,\feval)
            \in \SIG[\uid] \\
            % \textrm{Parse}~\Sig~\textrm{as}~(\sig,\yeval,\ceval) \\
            (\yinsp,\iproof) \gets
            SimOpen(\PRVOK[\oid],\PUBIK[\scid],\Sig,\msg,\feval) \\
            \pcif \CSIG[\Sig] \neq \bot: \\
            \pcind \textrm{Parse $\CSIG[\Sig]$ as $(\oid,\cuid_b,\scid_b,\msg,
              \feval$} \\
            \hspace*{83pt}\cuid_{1-b},\cSig_{1-b},\scid_{1-b}) \\
            \pcind (\yinsp',\iproof') \gets
            \Open(\PRVOK[\oid],\IK[\siid],\\
            \hspace*{107pt} \cSig_{1-b},\msg,\feval) \\
            \pcind \pcif \yinsp' \neq \yinsp: \pcreturn \bot \\
            \pcreturn (\yinsp,\iproof)          
          }
        \end{minipage}
        \begin{minipage}[t]{0.45\textwidth}
          \procedure{$SimOpen(\opk,\msg,\feval)$}{%
          }
        \end{minipage}
      \end{minipage}    
    \end{minipage}
    \label{fig:sim-anon}
    \caption{Definition of \SimSetup, \SIMOBTAIN, \SIMSIGN, and \SIMOPEN for
      anonymity in \CUASGen.}
  \end{figure}
  \fi

@@

\begin{theorem}[Issuance unforgeability of \CUASGen]
  \label{thm:issue-forge-uas}
  If the underlying NIZK used for $\NIZKRel_{\Issue}$ is zero-knowledge,
  simulation extractable and sound, then our \CUASGen construction satisfies
  issuance unforgeability as defined in \defref{def:issue-forge-uas}.
\end{theorem}

@@

\begin{theorem}[Signing unforgeability of \CUASGen]
  \label{thm:sign-forge-uas}
  If the underlying NIZK scheme for $\NIZKRel_{\Sign}$ is simulation
  extractable,the NIZK scheme for $\NIZKRel_{\Open}$ is complete, the public-key
  encryption scheme is correct, and \SBCM is correct and one-more unforgeable,
  then our \CUASGen construction satisfies signing unforgeability as defined in
  \defref{def:sign-forge-uas}, except with negligible probability.
\end{theorem}

\begin{proof}[\thmref{thm:sign-forge-uas}; Sign unforgeability of \CUASGen]
  As in \thmref{thm:issue-forge-uas}, we define two games, $G_0=\ExpForgeSign$,
  and $G_1$, which is exactly the same but where, within the \Setup algorithm,
  we replace $\NIZKSetup^{\Sign}$ with $\NIZKSimSetup^{\Sign}$. After
  zero-knowledgeness of $\NIZK^{\Sign}$, both games are indistinguishable.
  %
  Next, we show that an adversary winning $G_1$ can be used to break the
  one-more unforgeability property of \SBCM.

@@

\begin{theorem}[Non-frameability of \CUASGen]
  \label{thm:frame-uas}
  If the underlying scheme for $\NIZK^{\Issue}$ is zero-knowledge, the schemes
  for $\NIZK^{\Sign}$ are zero-knowledge and simulation-extractable, and the
  commitment scheme is hiding, then our \CUASGen construction satisfies
  non-frameability as defined in \defref{def:frame-uas}, except with negligible
  probability.
\end{theorem}

\begin{proof}[\thmref{thm:frame-uas}; Non-frameability of \CUASGen]
  We prove that, given an adversary $\adv$ against non-frameability of
  \CUASGen, we can build an adversary \advB that breaks the hiding property of
  the underlying commitment scheme, with non-negligible probability.

  We start from $G_0=\ExpNonframe$. $\adv$ makes queries to the oracles in
  \Oframe. For $G_1$, within \Setup, we replace the \Setup algorithms for the
  three NIZKs (\Issue, \Sign and \Open) with their corresponding \SimSetup
  variants. Consequently, the corresponding queries to \Prove are also
  simulated via the simulator. By the zero-knowledge property of the NIZK
  systems, $G_1$ is indistinguishable from $G_0$. In the sequel, we build on
  top of $G_1$, depending on whether or not a matching \Sig is found in \SIG,
  in line 7.

  \paragraph{(a) A matching \Sig exists in \SIG.} %
  If we can find a matching \Sig in \SIG, for some \uid, then \adv~does not win
  at line 7 of the game. Given that the signature is accepted by \Verify at line
  3, and after simulation extractability of $\NIZK^{\Sign}$, $\yeval =
  \yeval^0$, and $\tyeval^1 = \yeval^1$. Similarly, since the $(\yinsp,\iproof)$
  pair output by \adv~is accepted by \Judge, simulation extractability of
  $\NIZK^{\Sign}$ and $\NIZK^{\Open}$ implies that both checks at line 9 pass.
  Hence, the probability that the adversary wins at either lines 8 or 9 is $0$,
  after simulation extractability of $\NIZK^{\Sign}$ and $\NIZK^{\Open}$.

  \paragraph{(b) No matching \Sig exists in \SIG.} %
  This means that \adv~creates an \UAS forgery. We leverage such an adversary
  against $G_1$ to break the hiding property of the underlying commitment
  scheme (see \appref{sapp:commitments}). For each new honest user \uid creation
  request by \adv~(via \HUGEN),
  \advB leverages its own $COM$ oracle to embed its challenges in the commitment
  scheme into credentials of the \UAS non-frameability game. More precisely, in
  calls to \HUGEN by \adv, \advB does not call \UKeyGen and instead picks two
  random messages, $\msg_0^{\uid},\msg_1^{\uid}$, both from \AttrSpace. Whenever
  a query to \OBTAIN is made by \adv~on behalf of \uid, \advB makes a call to
  its $COM$ oracle, to get a commitment \Ccom for $\usk^{\uid}=\msg_b^{\uid}$
  (for \advB's challenge bit $b$). Then,  \advB uses \Ccom in its \SBCMCom part
  of the underlying \SBCM interactive signing protocol, and simulates the
  corresponding $\NIZK^{\Issue}$ proof. Due to the zero-knowledge property, the
  produced output is indistinguishable to that of the real execution. Similarly,
  \advB can simulate the calls to the \SIGN and \OPEN oracles due to
  simulation extractability of $\NIZK^{\Sign}$ and $\NIZK^{\Open}$.
  %
  Eventually, $\adv$ outputs a $(\oid,\siid,\Sig,\msg,\feval,\yinsp,\iproof)$
  tuple that is accepted by \Verify and \Judge. Due to simulation extractability
  of $NIZK^{\Sign}$, \ExtractSign must be able to produce a $(\usk,\scred,
  \attrs_{\scred}, \tyeval^1,\yinsp')$ tuple. As, by assumption (line 6),  there
  exists an \uid matching that \usk, all \advB has to do is find the
  \uid for which \usk was used as either $\msg_0$ or $\msg_1$ in its hiding
  game. Thus, \advB wins its hiding game with the same probability than \adv~
  has to win the non-frameability game.
  %
  \qed
\end{proof}

%%% Local Variables:
%%% mode: latex
%%% TeX-master: "uas"
%%% End:

>>>>

\section{Correctness and Security Proofs for \CUASGen}
\label{app:uas-proofs}

First, we define the \SimSetup, \ExtractIssue, \ExtractSign, \IdentifyCred and
\IdentifyUK functions that are needed for some of the properties to be
meaningful, in \figref{fig:helper-funcs}.

\begin{figure}[ht!]
  \scalebox{0.9}{
    \begin{minipage}[t]{\textwidth}
      \procedure{$\SimSetup(1^\secpar)$}{%
        \textrm{Parse}~\secpar~\textrm{as}~(\Csecpar,\NIZKsecpar,\SBCMsecpar,
        \Esecpar). \\
        \Cparm \gets \CSetup(\Csecpar), \SBCMparm \gets  \SBCMSetup(\SBCMsecpar) \\
        \Sparm \gets \SSetup(\Ssecpar), \Eparm \gets \ESetup(\Esecpar) \\
        (\NIZKcrs_{\Issue},\trap_{\Issue}) \gets
        \NIZKSimSetup^{\NIZKRel_{\Issue}}(\NIZKsecpar) \\
        (\NIZKcrs_{\Sign},\trap_{\Sign}) \gets
        \NIZKSimSetup^{\NIZKRel_{\Sign}}(\NIZKsecpar) \\
        (\NIZKcrs_{\Open},\trap_{\Open}) \gets
        \NIZKSimSetup^{\NIZKRel_{\Open}}(\NIZKsecpar) \\
        \pcreturn ((\Cparm,\SBCMparm,\Sparm,\Eparm,\NIZKcrs_{\Issue},
        \NIZKcrs_{\Sign},\NIZKcrs_{\Open},\AttrSpace), \\
        \pcind (\trap_{\Issue},\trap_{\Sign},\trap_{\Open})) \\
      }

      \procedure{$\ExtractIssue(\parm,\trap,\utrans)$}{%
        \textrm{Parse \parm as $(\cdot,\cdot,\cdot,\cdot,\NIZKcrs_{\Issue},\cdot,
          \cdot,\cdot)$} \\
        \textrm{Parse \trap as $(\trap_{\Issue},\cdot,\cdot)$, and
          \utrans as $(\Ccom,\sipk,\cred,\NIZKproof)$} \\
        \pcif \NIZKVerify^{\NIZKRel_{\Issue}}(\NIZKcrs_{\Issue},
        \NIZKproof,(\Ccom,\attrs,\sipk)): \pcreturn \bot \\
        (\usk,\scred,\attrs_{\scred}) \gets
        \NIZKExtract^{\NIZKRel_{\Issue}}(\NIZKcrs_{\Issue},
        \trap_{\Issue},
        (\Ccom,\attrs,\sipk),\NIZKproof) \\
        \pcreturn (\usk,\attrs,\scred,\attrs_{\scred}) \\
      }

      \procedure{$\ExtractSign(\parm,\trap,\oid,\siid,\sig,\yeval,\msg,\feval)$}{%
        \textrm{Parse \parm as $(\cdot,\cdot,\cdot,\cdot,\cdot,\NIZKcrs_{\Sign},
          \cdot)$} \\
        \textrm{Parse \trap as $(\cdot,\trap_{\Sign},\cdot)$, and
          \sig as $(\NIZKproof,\ceval,\cinsp)$} \\
        \textrm{Parse $\PUBOK[\oid]$ as $(\opk,\cdot)$ and let $\sipk \gets
          \PUBIK[\siid]$} \\
        \pcif \NIZKVerify^{\NIZKRel_{\Sign}}(\NIZKcrs_{\Sign},\NIZKproof,
        (\msg,\feval,\yeval,\Ec,\sipk,\opk)): \pcreturn \bot \\
        (\usk,\scred,\attrs_{\scred},\yinsp,r) \gets
        \NIZKExtract^{\NIZKRel_{\Sign}}(\NIZKcrs^{\NIZKRel_{\Sign}},
        \NIZKtrap_{\Sign},
        (\msg,\feval,\yeval^0,\ceval,\cinsp,\sipk,\opk,\widetilde{\Eek}),
        \NIZKproof) \\
        \pcreturn (\usk,\scred,\attrs_{\scred},\yeval^1,\yinsp) \\
      }

      \procedure{$\IdentifyCred(\parm,\trap,\usk,\attrs_{\cred},\cred)$}{%
        \pcreturn \SBCMVerify(\ipk_{\cred},\cred,\usk,\attrs_{\cred}) \\
      }

      \procedure{$\IdentifyUK(\parm,\trap,\uid,\usk)$}{%
        \pcif \uid \in \HU: \pcreturn \usk = \UK[\uid] \\
        \pcfor \cid~\suchthat~\CRED[\cid] = (\uid,\cdot,\cdot,\cdot,\cdot,\cdot) \\
        \pcind (\usk',\cdot,\cdot,\cdot) \gets \ExtractIssue(\parm,\trap,\trans[\cid]) \\
        \pcind \pcif \usk = \usk': \pcreturn 1 \\
        \pcreturn 0
      }
    \end{minipage}
  }
  \label{fig:helper-funcs}
  \caption{Definition of helper functions \ExtractIssue, \ExtractSign,
    \IdentifyCred, and \IdentifyUK, for \CUASGen.}
\end{figure}

\subsection{Correctness}

@@

\subsection{Issuance Anonymity}

\begin{proof}[\thmref{thm:issue-anonymity-uas}; Issuance anonymity of \CUASGen]
  We prove the special case in which the adversary makes only one query to the
  \OBTCHALb oracle. The generalization to polynomially many queries follows from
  a standard hybrid argument.

@@

\subsection{Signature Anonymity}

\begin{proof}[\thmref{thm:sign-anonymity-uas}; Signature anonymity of \CUASGen]

@@

\subsection{Issuance Unforgeability}

@@

\subsection{Signature Unforgeability}

\begin{proof}[\thmref{thm:sign-forge-uas}; Signature unforgeability of \CUASGen]
  As in \thmref{thm:issue-forge-uas}, we define two games, $G_0=\ExpForgeSign$,
  and $G_1$, which is exactly the same but where, within the \Setup algorithm,
  we replace $\NIZKSetup^{\Sign}$ with $\NIZKSimSetup^{\Sign}$. After
  zero-knowledgeness of $\NIZK^{\Sign}$, both games are indistinguishable.
  %
  Next, we show that an adversary winning $G_1$ can be used to break the
  one-more unforgeability property of \SBCM.

@@

\subsection{Non-Frameability}

\begin{proof}[\thmref{thm:frame-uas}; Non-frameability of \CUASGen]

  % We prove that, if the NIZK system used for $\NIZKRel_{\Sign}$ and
  % $\NIZKRel_{\Open}$ is zero-knowledge and simulation-extractable, and \SBCM is
  % blind, then our \CUASGen construction is secure.

  First, suppose that the \Sig that \adv~outputs at line 2 exists in
  \SIG, for some \uid. Then, Given that the signature is accepted by \Verify at
  line 3, and after simulation extractability of $\NIZK^{\Sign}$, $\yeval =
  \yeval^0$, and $\tyeval^1 = \yeval^1$. Similarly, since the $(\yinsp,\iproof)$
  pair output by \adv~is accepted by \Judge, simulation extractability of
  $\NIZK^{\Sign}$ and $\NIZK^{\Open}$ implies that both checks at lines 8 and 9
  pass. Hence, the probability that the adversary wins at either lines 8 or 9 is
  negligible, after simulation extractability of $\NIZK^{\Sign}$ and
  $\NIZK^{\Open}$.

  Next, suppose that the \Sig output by \adv~at line 2 does not exist in \SIG.
  We prove that zero-knowledge and simulation extractability of
  $\NIZKRel_{\Sign}$, and blindness of \SBCM, ensure that this only happens with
  negligible probability.
  The crucial observation is that, as in \cite{cl06} \CUASGen's \Sign algorithm
  produces a signature of knowledge for the relation defined by
  $\NIZKRel^{\Sign}$. That is, given $(x,w) \in \NIZKRel^{\Sign}$, one can
  compare $x$ and $w$ to the public and private key of a signature algorithm,
  respectively. In $\NIZKRel^{\Sign}$, $(\usk,\scred,\attrs_{\scred},\yeval^1,
  \yinsp,r,r')$ is the private key ($w$), and $(\msg,\feval,\yeval^0,\ceval,
  \cinsp,\sipk_{\scred},\Eek,\widetilde{\Eek})$ is the public key ($x$).
  %
  From this, we prove that an adversary has only negligible probability to forge
  a signature as originating from an honest user without calling the \SIGN
  oracle. The strategy is similar to that in \cite[Theorem 2.1]{cl06}.

  Consider game $G_1$, which is equivalent to $G_0 = \ExpNonframe$, except that
  in the \Sign function within the \SIGN oracle, we simulate the NIZK proof.
  After the zero-knowledge property of $\NIZK^{\NIZKRel_{\Sign}}$, $G_1$ is
  indistinguishable from $G_0$. Now, in $G_1$, simulation extractability of
  $\NIZK^{\NIZKRel_{\Sign}}$ ensures that \ExtractSign must output a valid
  witness for $(\msg,\feval,\yeval^0,\ceval,\cinsp,\sipk_{\scred},\Eek,
  \widetilde{\Eek})$. Note that this witness must include some \usk which,
  for \adv~to win the game, must belong to an honest user. However, since the
  user (whichever it is) has not been corrupted, its \usk has not been leaked
  to \adv~via corruption queries (nor via \SIGN queries, where the proof of
  knowledge within \Sign is now simulated). Moreover, blindness of \SBCM ensures
  that the issuer (who is potentially corrupt), did not learn \usk either during
  calls to \OBTAIN. Thus, the probability that $\UK[\uid] = \usk$ for $\uid \in
  \HU$ and \Sig produced by the adversary, is negligible.
  %
  \qed
\end{proof}

%%% Local Variables:
%%% mode: latex
%%% TeX-master: "uas-paper"
%%% End:
